### 2023-07-12 intro.tex
Rename unbound stuff to free

Consider, for example, the ill-typed program below, which is shown as presented to the user in
this paper's version of Hazel \cite{hazel}, a typed functional dialect of Elm \cite{elm}. Hazel  
supports local type inference, specified in the well-established bidirectional style \cite{Localinf,HazelnutPOPL,BidirTyping}:
\vspace{-3px}
\begin{center}
    \includegraphics[scale=0.5]{images/hazel-intro-screenshot-v3.png}
\end{center}
\vspace{-3px}
A type checker with no support for error localization or recovery---%
as students in an undergraduate course might write---%
would simply report that this program is ill-typed. 
A more practical approach, and one common even in production type checkers, 
is to localize the first error that causes local type inference to fail and emit an explanatory error message before terminating.
In this example, the system might report that the variable \li{f} located on Line 2 is unbound, then terminate.

An implementation with support for type error recovery, like Elm's compiler or OCaml's \li{merlin} \cite{bour2018merlin}, would 
 be tasked with continuing past this first error.
 The general difficulty here is that there is now missing semantic information, namely the type of \li{f}, that 
 the bidirectional type system as specified 
 would appear to demand in order to proceed, here in order to determine which type the argument, \li{y}, is to be analyzed against. 
 Intuitively, however, it is clear that this knowledge is \emph{unnecessary} to make an error localization decision about \li{y}: 
it is unbound, so a second error can be simultaneously localized despite the missing information about \li{f}.

>>>>

Consider, for example, the ill-typed program below, which is shown as presented to the user in
this paper's version of Hazel \cite{hazel}, a typed functional dialect of Elm \cite{elm}. Hazel  
supports local type inference, specified in the well-established bidirectional style \cite{Localinf,HazelnutPOPL,BidirTyping}:
\vspace{-3px}
\begin{center}
    \includegraphics[scale=0.5]{images/hazel-intro-screenshot-v3.png}
\end{center}
\vspace{-3px}
A type checker with no support for error localization or recovery---%
as students in an undergraduate course might write---%
would simply report that this program is ill-typed. 
A more practical approach, and one common even in production type checkers, 
is to localize the first error that causes local type inference to fail and emit an explanatory error message before terminating.
In this example, the system might report that the variable \li{f} located on Line 2 is free, then terminate.

An implementation with support for type error recovery, like Elm's compiler or OCaml's \li{merlin} \cite{bour2018merlin}, would 
 be tasked with continuing past this first error.
 The general difficulty here is that there is now missing semantic information, namely the type of \li{f}, that 
 the bidirectional type system as specified 
 would appear to demand in order to proceed, here in order to determine which type the argument, \li{y}, is to be analyzed against. 
 Intuitively, however, it is clear that this knowledge is \emph{unnecessary} to make an error localization decision about \li{y}: 
it is free, so a second error can be simultaneously localized despite the missing information about \li{f}.
